HO unification from object language to meta language

### 2024-02-21 paper/main.tex
update tex

\section[Compilation: fo\_tm to tm]{Compilation: \texttt{tm} $\to$ \texttt{tm}}

% - how we transform an fo\_tm in tm \\
% - the role of links \\
% - decomp
% - esempio che va in questa semplice rappresentazione (from intro)
% - esempio che non va, multi-var, eta, beta
% % \section{Term de-compilation}

% \section{Unification in ML}

% - we accept HO unif with PF \\
% - need of multiple vars for a single OL var

% % Compile FO to HO

% % Assignement in HO should be decompiled

>>>>

\section[Compilation: fo\_tm to tm]{Compilation}

The compilation step is meant to recover the higher-order variables of the OL,
expressed in a first order way, by replacing them with higher-order variables in
the ML. In particular, every time a variable of the OL is encountered in the
original term, it is replaced with a meta variable, and if the OL variable is
applied to a list $L$ of terms, then this list becomes the scope of the variable
if $L$ is a list of distinct names. For all the other constructors of
\elpiIn{tm}, the same term constructor is returned and its arguments are
recursively compiled. The predicate in charge for term compilation is:\\
\elpiIn{type comp tm -> tm -> links -> links -> subst -> subst -> o}.
Where, we take the term of the OL, produce the term of the ML, take a list
of link and produce a list of new links, take a substitution and return a 
new substitution.

In particular, due to programming constraints, we need to drag the old subst and
return a new one extended, if needed, with the new declared meta-variables.

The following code
\begin{elpicode}
  kind link type.
  type link nat -> nat -> nat -> subst.
\end{elpicode}

\noindent
defines a link, which is a relation between to variables indexes, the first
being the index of a OL variable and the second being the index of a ML
variable. The third integer\todo{integer or nat?} is the number of term in the
scope of the two variables, or equivalently, in a typed language, their arity.

\noindent
- how we transform an fo\_tm in tm \\
- the role of links \\
- decomp
- esempio che va in questa semplice rappresentazione (from intro)
- esempio che non va, multi-var, eta, beta
% \section{Term de-compilation}

\section{Unification in ML}

- we accept HO unif with PF \\
- need of multiple vars for a single OL var

% Compile FO to HO

% Assignement in HO should be decompiled
